Classless Java

### 2015-11-10 paper/sections/CaseStudy.tex
Setters and clone
UnitTest.

\lstinputlisting[linerange=23-40]{../UseMixinLombok/src/test/TestExpression.java}% APPLY:linerange=EXPRESSION_INIT

@@

\lstinputlisting[linerange=44-51]{../UseMixinLombok/src/test/TestExpression.java}% APPLY:linerange=EXPRESSION_SUB

@@

\lstinputlisting[linerange=55-73]{../UseMixinLombok/src/test/TestExpression.java}% APPLY:linerange=EXPRESSION_PRINT

@@

\subsection{Other case studies}

Other case studies using multiple inheritance?

>>>>

\lstinputlisting[linerange=25-42]{../UseMixinLombok/src/test/TestExpression.java}% APPLY:linerange=EXPRESSION_INIT

@@

\lstinputlisting[linerange=46-53]{../UseMixinLombok/src/test/TestExpression.java}% APPLY:linerange=EXPRESSION_SUB

@@

\lstinputlisting[linerange=57-75]{../UseMixinLombok/src/test/TestExpression.java}% APPLY:linerange=EXPRESSION_PRINT

@@

\subsection{Other case studies}
\marco{should we put here the DB with fluent setters?}
